### 2020-04-24 manuscript.rmd
Manuscript formatting.

## Affiliations  
1 - Division of Infectious Diseases, Department of Medicine;  
2 - Department of Biostatistics, Epidemiology, and Informatics;  
Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA;  
3 - Department of Medicine, University of Colorado, Aurora, CO;  
4 - Division of Infectious Diseases, Mount Sinai School of Medicine, New York, NY

@@

### Materials and Methods  
#### Study Design  
We performed a case-crossover study to define the relationship between the quantity of sputum production (primary exposure), measured as the frequency with which nurses and respiratory therapists chose to perform as-needed subglottic suctioning, and the occurrence of VAE (primary outcome). We also analyzed whether VAE were categorized as VAC without suspected infection or as IVAC. For the primary anlysis, the day of VAE was the case period; the days prior to VAE were the control periods.

@@

>>>>

## Affiliations  
1 - Division of Infectious Diseases, Department of Medicine;  
2 - Department of Biostatistics, Epidemiology, and Informatics;  
Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA;  
3 - Department of Medicine, University of Colorado, Aurora, CO;  
4 - Division of Infectious Disease, Department of Medicine, Icahn School of Medicine at Mount Sinai, New York, NY

@@

### Materials & Methods  
#### Study Design  
We performed a case-crossover study to define the relationship between the quantity of sputum production (primary exposure), measured as the frequency with which nurses and respiratory therapists chose to perform as-needed subglottic suctioning, and the occurrence of VAE (primary outcome). We also analyzed whether VAE were categorized as VAC without suspected infection or as IVAC. For the primary anlysis, the day of VAE was the case period; the days prior to VAE were the control periods.

@@

### Conclusions  
The frequency of subglottic suction events, which are performed on an as-needed basis for patients dependent on mechanical ventilation, may serve as a valuable marker of sputum quantity, which is associated with risk for risk for adverse ventilator-associated events (VAE). However, the relationship between subglottic suction events, sputum quantity, and VAE must be validated in a broader population of mechanically ventilated patients and intensive care settings.
